Table on stock change factors per clinate zone

### 2022-07-20 ResultNotebooks/results_SOCtable.Rmd
update to version before bug check

cols <- c("#648FFF", "#DC267F", "#FFB000")[3:1]

SCFTable <- 
  ggplot() + 
    geom_linerange(data = range_table,
                   aes(x = Region, ymin = Q0p05, ymax = Q0p95, color = Source),
                   position = position_nudge(x = 0.165), size = 0.6) +
    geom_point(data = comparison_table, 
               aes(y = Data, x = Region, group = Source, color = Source, shape = Management), 
               position = position_dodge(width = 0.5), 
               size = 2) +
    labs(y = "Stock Change Factor",
         x = "Climate Zone") +
    scale_color_manual(values = cols) +
    guides(shape = guide_legend(order = 2),col = guide_legend(order = 1)) +
    theme(rect = element_blank(),
                        axis.title.y = element_text(size = legend_size,
                                                   margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                                   unit = "pt")),
                        axis.title.x = element_text(size = legend_size,
                                                   margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                                   unit = "pt")))

>>>>

cols        <- c("#648FFF", "#DC267F", "#FFB000")[3:1]
legend_size <- 12

SCFTable <- 
  ggplot() + 
    geom_linerange(data = range_table,
                   aes(x = Region, ymin = Q0p05, ymax = Q0p95, color = Source),
                   position = position_nudge(x = 0.165), size = 0.6) +
    geom_point(data = comparison_table, 
               aes(y = Data, x = Region, group = Source, color = Source, shape = Management), 
               position = position_dodge(width = 0.5), 
               size = 2) +
    labs(y = "Stock Change Factor",
         x = "Climate Zone") +
    scale_color_manual(values = cols) +
    scale_x_discrete(labels = c("tropical\nmoist", "tropical\ndry", 
                                "temperate\ndry",  "temperate\nmoist")) +
    guides(shape = guide_legend(order = 2),col = guide_legend(order = 1)) +
    theme(rect = element_blank(),
          axis.title.y = element_text(size = legend_size,
                                      margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                                   unit = "pt")),
          axis.title.x = element_text(size = legend_size,
                                      margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                                   unit = "pt")),
          axis.text.x  = element_text(size = legend_size),
          axis.text.y  = element_text(size = legend_size),
          legend.title = element_text(size = legend_size),
          legend.text  = element_text(size = legend_size),
          legend.spacing.y = unit(0.1, "cm"))

SCFTable
